CommonMind Consortium: DLPFC

### 2020-09-18 combined_analysis/diff.networks.Rmd
Update diff networks

# NULL network

# Sex network
## Difference networks
```{r diff.networks.null}

@@

p = df_test$P.Value[df_test$Cohort== "NIMH-HBCC"]
data.frame(pi1 = 1 - qvalue(p)$pi0, "# DE" = sum(p.adjust(p, 'fdr') < 0.05)) %>% kable
hist(p)
```

@@

>>>>

# Null network

```{r diff.networks.null}

@@

p = df_test$P.Value[df_test$Cohort== "NIMH-HBCC"]
data.frame("# DE" = sum(p.adjust(p, 'fdr') < 0.05), check.names=FALSE) %>% kable
hist(p)
```

@@

```{r exit, cache=FALSE}
knitr::knit_exit()
```
